Final Project Code ALL

### 2022-12-08 Draft_Final_Code.Rmd
Organized RF Code

# Bagging and Random Forests

@@

@@

@@

@@

### Evaluating the Forest

@@

@@

@@

model_output2 %>% vip::vi() %>% head()
model_output2 %>% vip::vi() %>% tail()
```
```{r}
ggplot(imdb_clean_class, aes(x = flop, y = No_of_Votes)) +
    geom_violin() + theme_classic()

@@

# Logistic Regression

>>>>

# Classification Models

## Create New Dataset for Classification

@@

## Random Forests Model

### Model Spec, Recipe, and Workflow

@@

### Fit Models with Various Values for mtry

@@

### Obtain OOB Predictions and Evaluation Metrics

@@

### Evaluating Selected Model - Confusion Matrix

@@

#### Impurity

@@

#### Permuation

@@

model_output2 %>% vip::vi() %>% head()
model_output2 %>% vip::vi() %>% tail()
```

### Violin Graphs

```{r}
ggplot(imdb_clean_class, aes(x = flop, y = No_of_Votes)) +
    geom_violin() + theme_classic()

@@

## Logistic Regression
